On Secure Delegation of SampBQP with a Classical Client

### 2020-02-05 bqp.tex
Editorial and macros change

Now we compile \cref{proto:BQP} using $\mathsf{QHE}$ in order to achieve blindness.
We denote the honest prover's action in $\cref{proto:BQP}$ as $\cF$; that is, $\cF(x)=\ket{\psi_x}^{\otimes 2n}$.

\begin{protocol}{Blind Protocol for $\BQP$}
	\label{proto:BlindBQP}
	Let $\lambda$ be the security parameter.
	Let $L$ be the depth of the circuit corresponding to $\cF$.
	Let $n$ be number of repetitions required to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
	\begin{enumerate}
		\item The verifier runs $\mathsf{QHE.Keygen}(\lambda, L)$ to get $pk, sk$.
		\item The verifier encrypts $x$ to get $\mathsf{QHE.Enc}_{pk}(x)$
		\item The verifier sends $c=\mathsf{QHE.Enc}_{pk}(x)$ and $pk$ to the prover
		\item The prover sends $\mathsf{QHE.Eval}(\cF, c)$ to the verifier
		\item The verifier measures the incoming ciphertext according to \autoref{decodeMeasureOrder} and how it would've checked the $\QMA$ certificates \Ethan{Not sure if rigorous enough}
		\item The verifier decodes the measurement results
		\item The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
	\end{enumerate}
\end{protocol}

>>>>

Now we compile \cref{proto:BQP} using $\mathsf{QHE}$ in order to achieve blindness.
We denote the honest prover's action in \cref{proto:BQP} as $\cF$; that is, $\cF(x)=\ket{\psi_x}^{\otimes 2n}$.

\begin{protocol}{Blind Protocol for $\BQP$}
	\label{proto:BlindBQP}
	Let $\lambda$ be the security parameter.
	Let $L$ be the depth of the circuit corresponding to $\cF$.
	Let $n$ be number of repetitions required to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
	\begin{enumerate}
		\item The verifier runs $\mathsf{QHE.Keygen}(\lambda, L)$ to get $pk, sk$.
		\item The verifier encrypts $x$ to get $\mathsf{QHE.Enc}_{pk}(x)$
		\item The verifier sends $c=\mathsf{QHE.Enc}_{pk}(x)$ and $pk$ to the prover
		\item The prover sends $\mathsf{QHE.Eval}(\cF, c)$ to the verifier
		\item The verifier measures the incoming ciphertext according to \cref{decodeMeasureOrder} and how it would've checked the $\QMA$ certificates \Ethan{Not sure if rigorous enough}
		\item The verifier decodes the measurement results
		\item The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
	\end{enumerate}
\end{protocol}
